Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-22 paper/paper.qmd
committing text changes to idealized methodology appendix section

```{r}
#| label: barplot-diagnostics
#| fig-cap: "Model: Diagnostics: Accuracy and RMSE"
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@

# Idealized Methodology
To represent our idealized methodology, we generated a survey on the 2024 US Presidential election, which can be accessed via [@US-election-survey].

@@

For recruiting participants, we will begin by sending survey invitations to our selected voters via email, offering a $20 incentive to encourage participation. To improve response rates and reduce non-response bias, we will send a reminder email three days later. This approach helps minimize labor costs to some extent. If we do not receive a response within a week(7 days), we will follow up by phone to reach those who did not respond to the email invitation.

>>>>

```{r}
#| echo: false
#| eval: true
#| label: barplot-diagnostics
#| fig-cap: "Model: Diagnostics: Accuracy and RMSE"
#| warning: false
#| message: false

@@

# Idealized Methodology

Building on our discussion of the New York Times/Siena College Poll, we now present an idealized methodology that aims to enhance the accuracy and reliability of our predictions. This approach incorporates best practices and innovative techniques to ensure a comprehensive prediction of voter behavior in the upcoming 2024 U.S. presidential election. To represent our idealized methodology, we generated a survey on the 2024 US Presidential election, which can be accessed via [@US-election-survey].

@@

For recruiting participants, we will begin by sending survey invitations to our selected voters via email, offering a $20 incentive to encourage participation. To improve response rates and reduce non-response bias, we will send a reminder email three days later. This approach helps minimize labor costs to some extent. If we do not receive a response within a week (7 days), we will follow up by phone to reach those who did not respond to the email invitation.
